Pruning Subsequence Search with Attention-Based Embedding

### 2015-09-24 paper.tex
Remove some references to make it fit

At a high level, attention-based models are similar to the common technique of summarizing a sequence of feature vectors by the mean, variance, and occasionally covariance of feature dimensions.
This simple approach has seen frequent application in the domain of music information retrieval, where it has proven to be surprisingly effective at genre classification \cite{bergstra2006aggregate, tzanetakis2002musical}, instrument classification \cite{deng2008study}, artist recognition \cite{mandel2005song}, and similarity rating prediction \cite{foster2014sequential}.
Attention-based models can be seen as a generalization of this technique where both the feature representation and a weighted average are both optimized and data-adaptive.

@@

To choose hyperparameter settings, we used the Bayesian optimization software package \texttt{spearmint} \cite{snoek2012practical}.
We optimized the number of convolutional and pooling layers, the number of fully-connected layers, the learning rate and momentum, and the loss parameters $\alpha$ and $m$.
We also experimented with using RMSProp \cite{tieleman2012lecture} and adam \cite{kingma2014adam} for optimization and dropout \cite{hinton2012improving} in the fully-connected layers for regularization, but did not find them to be beneficial.
As an objective, we computed the Bhattacharrya coefficient \cite{bhattacharyya1943measure} between the distributions of matching and non-matching pairs in the validation set.
The best-performing network configuration achieved a Bhattacharrya coefficient of .471 and used a single convolutional layer with 16 filters which were 5 time steps wide by 12 semitones tall, one 2x2 max-pooling layer, two fully connected hidden layers with 2048 units each, a learning rate of $10^{-4}$, a momentum of 0.997, $\alpha = 0.935$ and $m = 1$.
The validation set distance distributions produced by this network after training can be seen in Figure \ref{fig:distances}.

>>>>

At a high level, attention-based models are similar to the common technique of summarizing a sequence of feature vectors by the mean, variance, and occasionally covariance of feature dimensions.
This simple approach has seen frequent application in the domain of music information retrieval, where it has proven to be surprisingly effective at genre classification \cite{tzanetakis2002musical}, instrument classification \cite{deng2008study}, artist recognition \cite{mandel2005song}, and similarity rating prediction \cite{foster2014sequential}.
Attention-based models can be seen as a generalization of this technique where both the feature representation and a weighted average are both optimized and data-adaptive.

@@

To choose hyperparameter settings, we used the Bayesian optimization software package \texttt{spearmint} \cite{snoek2012practical}.
We optimized the number of convolutional and pooling layers, the number of fully-connected layers, the learning rate and momentum, and the loss parameters $\alpha$ and $m$.
We also experimented with using dropout \cite{hinton2012improving} in the fully-connected layers for regularization, but did not find it to be beneficial.
As an objective, we computed the Bhattacharrya coefficient \cite{bhattacharyya1943measure} between the distributions of matching and non-matching pairs in the validation set.
The best-performing network configuration achieved a Bhattacharrya coefficient of .471 and used a single convolutional layer with 16 filters which were 5 time steps wide by 12 semitones tall, one 2x2 max-pooling layer, two fully connected hidden layers with 2048 units each, a learning rate of $10^{-4}$, a momentum of 0.997, $\alpha = 0.935$ and $m = 1$.
The validation set distance distributions produced by this network after training can be seen in Figure \ref{fig:distances}.
